Bounded Model Checking for Embedded Systems \\ (Position Paper)

### 2016-03-18 paper.tex
review research problem

This position paper tackles four major problems in computer-aided verification for embedded systems: (RP1) providing suitable encoding into the Satisfiability Modulo Theories (SMT) \cite{BarrettSST09}, which may extend the background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic embedded programs, (RP2) exploiting SMT techniques to leverage bounded model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving, (RP3) proving correctness and timeliness of embedded systems, by taking into account stringent constraints imposed by hardware, and (RP4) incorporating knowledge about system purpose and associated features, which aims to detect system-level and behavior failures.

>>>>

This position paper tackles four major problems in computer-aided verification for embedded systems, which are (partially) open in present research.

\textbf{(RP1)} providing suitable encoding into the Satisfiability Modulo Theories (SMT) \cite{BarrettSST09}, which may extend the background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic embedded programs.

\textbf{(RP2)} exploiting SMT techniques to leverage bounded model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving.

\textbf{(RP3)} proving correctness and timeliness of embedded systems, by taking into account stringent constraints imposed by hardware.

\textbf{(RP4)} incorporating knowledge about system purpose and associated features, which aims to detect system-level and behavior failures.

Section~\ref{achievements} outlines contributions toward these research problems.
